---
title: "Build a ggplot"
author: "Francesco Lescai"
date: "28 May 2015"
output: slidy_presentation
---

## Choosing the data

We will select as data what is coming from a dataset package

```{r dataset}
library(ggplot2)
library(datasets)
```

And then we will select the dataset on chicken weights, which reports the weight of different chickens at different times with different type of diet

```{r chicken}
data(ChickWeight)
```


## Datasets

You can check the structure of the dataset by using

```{r structure}
str(ChickWeight)
```


## Datasets 2

or just by 

```{r structure2}
head(ChickWeight)
```


## Building the plot

We can first observe the data using a simple plot

```{r plotSimple}
ggplot(ChickWeight, aes(x=Time, y=weight, color=Diet))+geom_point()
```

which is a bit messy because at each timepoint we will have several individuals with different weights and different diets


## Building the plot 2

We can therefore use the smoothing function to estimate the trend by distinguishing the diets

```{r smoothPlot, message=FALSE}
ggplot(ChickWeight, aes(x=Time, y=weight, color=Diet))+geom_smooth()
```

This gives us a better idea that the diet 3 is the one that at the end seems to increase the weight of the chickens...
But we want to see this better

## Scales
we can therefore use the "scales" elemeent, to change the appearance of the legend and their names, and add to the geometry some more elements

```{r scalesModify}
ggplot(ChickWeight, aes(x=Time, y=weight, color=Diet))+
  geom_smooth(size=1)+
  scale_color_hue(
    "what do they \neat?", 
    breaks=c(1,2,3,4), 
    labels=c("carrots","peas","pasta","seeds")
    )
```

Et voilà
